Scalar and Representative Observables for Polarimetric SAR Data

### 2013-10-02 paper_dev/article_pp.tex
before going to work

%How do you know if the problem is solved? State your research contribution to be achieved
In summary, the main objective of this article is to propose the determinant of the POLSAR covariance matrix as a scalar observable
  that is representative of the multi-dimensional data.
Specifically the following research results are to be achieved:
  1. The generic scalar and representative statistical model for the determinant of the multi-dimensional POLSAR covariance matrix is to be derived, 
  2. This generic model is also shown leading to staititically consistent models for newly proposed POLSAR observables, namely the determinant-ratio and the change-ratio.
  3. The special one-dimensional version of the derived generic model is to be shown perfectly matches with the traditionally used SAR intensity model,
  4. All specific one, two and three dimensional versions of the derived generic model are to be validated against real-life captured data,
(Hai NOTE: I kept this to keep my focus while working on this paper.
  It can be removed before the final submission.)

%Article Organization: Show that you deliver on the objectives and hence solve the stated problem
The rest of this article is organized as follows.
After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR,
  section 3? derives the generic statistical model for the determinant of the POLSAR covariance matrix.
Section 4? then validates the specific two and three dimensional versions of the model against real-life captured data.
After section 5? illustrates the match between the specific model of one dimensional and the traditional model for SAR intensity,
  section 6? establishes the generic determinant-ratio descrimination measure which links the disparate discrimination measure proposals for the traditional SAR and the more recent POLSAR data.

@@

\section{Extending SAR data processing techniques towards POLSAR}

Currently while the field of SAR is much more developed than the field of POLSAR,
  the two fields however are quite separated.
Hence many techniques applicable to SAR are not directly applicable to POLSAR.
With the newly gained, the current proposal provide the bridge between these two separated fields,
  inviting potential extension of various SAR processing techniques to POLSAR data.
%For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
%  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
%We believe there are many more unexplored possibilities for such applications.

There are many beneficial implications for this proposal.
One of the main benefits is that:
  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
One example has already been presented in this paper, 
  where existing SAR discrimination measures are extended towards POLSAR.
Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.

In evaluating SAR speckle filters, the intensity ratio is widely used.
Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
Assuming a perfect filtering condition, the ratio image should only contain random noise.
Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.

Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
  this technique can be equally applied to evaluate POLSAR speckle filters.
In fact better results can be achieved.
In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
  which is linear and additive in nature.
Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
(TODO: shorten the above 2 paragraphs. 
NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)

To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
  and the two POLSAR speckle filters are then applied to the patch.
\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
		 \label{multi_look_contrast}
	} \\
	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
		 \label{multi_look_contrast}
	} 
\end{tabular}
\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
		 \label{multi_look_contrast}
	} \\
	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
		 \label{multi_look_contrast}
	} 
\end{tabular}
\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
\end{figure}
%endif

Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
  the distortion impact of the filter can also be made visible by the residual image.
In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
in the additive log-determinant image of the filtered output, 
  such an observation can be made relatively easier by inspecting the residual image.

There are many similar SAR data processing technique that may be adaptable to POLSAR.
Examples in the same topic of evaluating speckle filters include
  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.

>>>>

%How do you know if the problem is solved? State your research contribution to be achieved
%In summary, the main objective of this article is to propose the determinant of the POLSAR covariance matrix as a scalar observable
%  that is representative of the multi-dimensional data.
%Specifically the following research results are to be achieved:
%  1. The generic scalar and representative statistical model for the determinant of the multi-dimensional POLSAR covariance matrix is to be derived, 
%  2. This generic model is also shown leading to staititically consistent models for newly proposed POLSAR observables, namely the determinant-ratio and the change-ratio.
%  3. The special one-dimensional version of the derived generic model is to be shown perfectly matches with the traditionally used SAR intensity model,
%  4. All specific one, two and three dimensional versions of the derived generic model are to be validated against real-life captured data,
%(Hai NOTE: I kept this to keep my focus while working on this paper.
%  It can be removed before the final submission.)

%Article Organization: Show that you deliver on the objectives and hence solve the stated problem
Thus, the rest of this article is organized as follows.
After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR, section \ref{sec:theoretical_model}
  derives the generic statistical model for the determinant of the POLSAR covariance matrix
  and proposes several new discrimination measures for the multi-dimensional data.
After section \ref{sec:sar_special_case_of_polsar} illustrates the match between the specific model of one dimensional and the traditional model for SAR intensity,
  section \ref{sec:link_sar_polsar} links the disparate discrimination measure proposals for the traditional SAR and the more recent POLSAR data.
%Section \ref{sec:polsar_models_validation} then validates the specific one, two and three dimensional versions of the proposed model against real-life captured data.
The applicability of these models against practical data is illustrated in section \ref{sec:polsar_models_validation}.
Section \ref{sec:discussion} presents a high-level discussion of the results presented before
  section \ref{sec:conclusion} finally concludes this paper.

@@

%\section{Extending SAR data processing techniques towards POLSAR}
%
%Currently while the field of SAR is much more developed than the field of POLSAR,
%  the two fields however are quite separated.
%Hence many techniques applicable to SAR are not directly applicable to POLSAR.
%With the newly gained, the current proposal provide the bridge between these two separated fields,
%  inviting potential extension of various SAR processing techniques to POLSAR data.
%%For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
%%  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
%%We believe there are many more unexplored possibilities for such applications.
%  
%There are many beneficial implications for this proposal.
%One of the main benefits is that:
%  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
%One example has already been presented in this paper, 
%  where existing SAR discrimination measures are extended towards POLSAR.
%Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.  
%
%In evaluating SAR speckle filters, the intensity ratio is widely used.
%Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
%Assuming a perfect filtering condition, the ratio image should only contain random noise.
%Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.
%
%Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
%  this technique can be equally applied to evaluate POLSAR speckle filters.
%In fact better results can be achieved.
%In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
%  which is linear and additive in nature.
%Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
%(TODO: shorten the above 2 paragraphs. 
%NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)
%
%To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
%  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
%  and the two POLSAR speckle filters are then applied to the patch.
%\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
%  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
%  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
%The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
%At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
%
%%ifdef FINAL
%\begin{figure}[h]
%\centering
%\begin{tabular}{c}
%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
%		 \label{multi_look_dispersion}
%	} 
%	\hfill	
%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
%		 \label{multi_look_contrast}
%	} \\
%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
%		 \label{multi_look_dispersion}
%	} 
%	\hfill	
%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
%		 \label{multi_look_contrast}
%	} 
%\end{tabular}
%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
%\end{figure}
%%endif
%%ifdef REVIEW
%\begin{figure}[h!]
%\centering
%\begin{tabular}{c}
%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
%		 \epsfxsize=3in
%		 \epsfysize=3in
%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
%		 \label{multi_look_dispersion}
%	} 
%	\hfill	
%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
%		 \epsfxsize=3in
%		 \epsfysize=3in
%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
%		 \label{multi_look_contrast}
%	} \\
%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
%		 \epsfxsize=3in
%		 \epsfysize=3in
%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
%		 \label{multi_look_dispersion}
%	} 
%	\hfill	
%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
%		 \epsfxsize=3in
%		 \epsfysize=3in
%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
%		 \label{multi_look_contrast}
%	} 
%\end{tabular}
%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
%\end{figure}
%%endif
%
%Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
%  the distortion impact of the filter can also be made visible by the residual image.
%In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
%in the additive log-determinant image of the filtered output, 
%  such an observation can be made relatively easier by inspecting the residual image.
%  
%There are many similar SAR data processing technique that may be adaptable to POLSAR.
%Examples in the same topic of evaluating speckle filters include
%  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
%Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
